---
title: "PsyCorona Need Threat to Compensation"
author: "Maximilian Agostini, Anton Martinez"
date: "May 2020"
output:
  html_document:
    code_folding: hide
    mathjax: default
    theme: united
    toc: yes
    toc_float: yes
    number_sections: TRUE
  pdf_document:
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
cat("\014") # clear console
rm(list=ls()) # clear workspace
gc # garbage collector

require(pacman)
p_load(metafor, dplyr, tinytex, knitr, kableExtra, DescTools, reshape2, metaSEM, lavaan, semPlot, psych, ggplot2)

set.seed(52) # set overall random seed for reproducibility
```

# Load Data
```{r LoadRawBase, echo=T, warning=F, message=F}

# Import Data
dtRaw <- haven::read_spss(dir("data/raw data", pattern = "Agostini", full.names = TRUE, ignore.case = TRUE))
```

# Prepare Data
## Cleaning
```{r clean, echo=T, warning=F, message=F}
# change all -99 into NA
  dtRaw[dtRaw == -99] <- NA

# make relevant dfs
dtFull <- dtRaw
dtCtry <- dtRaw %>% 
  group_by(coded_country) %>% # group by country
  filter(n() > 200) # remove countries with less than 100 people
dtCtry <- dtCtry %>% #needs to be ungrouped for the scale calculation
  ungroup()
rm(dtRaw)
```

## Calculate relevant variables
```{r calcVars, echo=T, warning=F, message=F}
# positive emotion
  dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel) %>% psych::describe()
  dtCtry$PE.m <- scoreItems(keys=c(1,1,1,1,1),
                            items = dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel) %>% na_if(., -99),
                                min = 1, max = 5)$scores
  dtCtry$PE.c <- scale(dtCtry$PE.m, scale = F, center = T)
  dtCtry$PE.z <- scale(dtCtry$PE.m, scale = T)
  dtCtry$PE.fa <- fa(dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel))$scores

# Well-Being
  # need rescaling first
    dtCtry$lifeSat <- scales::rescale(as.numeric(dtCtry$lifeSat), to = c(1,10))
    dtCtry$MLQ <- scales::rescale(as.numeric(dtCtry$MLQ), to = c(1,10))
  dtCtry %>% dplyr::select(happy, lifeSat, MLQ) %>% psych::describe()
  dtCtry$WB.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(happy, lifeSat, MLQ) %>% na_if(., -99),
                                min = 1, max = 10)$scores
  dtCtry$WB.c <- scale(dtCtry$WB.m, scale = F, center = T)
  dtCtry$WB.z <- scale(dtCtry$WB.m, scale = T)
  dtCtry$WB.fa <- fa(dtCtry %>% dplyr::select(happy, lifeSat, MLQ))$scores

# pro-Social Behavior
  dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% psych::describe()
  dtCtry$c19ProSo.m <- scoreItems(keys=c(1,1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19ProSo.c <- scale(dtCtry$c19ProSo.m, scale = F, center = T)
  dtCtry$c19ProSo.z <- scale(dtCtry$c19ProSo.m, scale = T)
  dtCtry$c19ProSo.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")))$scores
  
# final step is grouping the data
  dtCtry <- dtCtry %>% 
    group_by(coded_country)
```

# Analysis
## Confirmatory Factor Analysis
### Simple Confirmatory Factor Analysis
```{r explrFactor12}
model <- '# Model 
            PE  =~ affCalm + affContent + affEnerg + affInsp + affRel 
            WB =~ happy + lifeSat + MLQ
            c19ProSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03 + c19ProSo04
          # Covariances
            PE ~~ WB
            PE ~~ c19ProSo
            WB ~~ c19ProSo'
fit <- cfa(model, data = dtCtry)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### MultiGroup Confirmatory Factor Analysis
```{r explrFactor}
# by country all
  fitGroup <- cfa(model, data = dtCtry, group = "coded_country")
  summary(fitGroup, fit.measures=TRUE)

# by country constrained
  #fitGroupConstr <- sem(model, dtCtry, group = "coded_country", group.equal = c("intercepts", "regressions"))
  
# compare unconstrained and constrained
  #anova(fitGroup, fitGroupConstr)
```

## MultiLevel Approach
### PE - Well-Being with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = PE.m, y = WB.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod1Fix <- lme4::lmer(WB.m ~ PE.c + (1|coded_country), data = dtCtry)
  summary(mod1Fix)
```

### PE - Well-Being with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = PE.m, y = WB.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod1Rand <- lme4::lmer(WB.m ~ PE.c + (1 + PE.c|coded_country), data = dtCtry)
  anova(mod1Fix, mod1Rand) # test diff
  summary(mod1Rand)
  sjPlot::plot_model(mod1Rand, type = c("re"), show.values = T, value.offset = .5)

```

### Pro-Social - Well-Being with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod2Fix <- lme4::lmer(WB.m ~ c19ProSo.c + (1|coded_country), data = dtCtry)
  summary(mod2Fix)
```

### ProSo - Well-Being with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod2Rand <- lme4::lmer(WB.m ~ c19ProSo.c + (1 + c19ProSo.c|coded_country), data = dtCtry)
  anova(mod2Fix, mod2Rand) # test diff
  summary(mod2Rand)
  sjPlot::plot_model(mod2Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### PE -ProSo - Well-Being with Fixed Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# plotly::ggplotly(tmp)

# fit model with random slope
  mod3Fix <- lme4::lmer(WB.m ~ c19ProSo.c + PE.c + (1|coded_country), data = dtCtry)
  summary(mod3Fix)
  sjPlot::plot_model(mod3Fix, type =  c("re"), show.values = T, value.offset = .5)
```

### PE -ProSo - Well-Being with Random Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# plotly::ggplotly(tmp)

# fit model with random slope
  mod3Rand <- lme4::lmer(WB.m ~ c19ProSo.c + PE.c + (1+ c19ProSo.c + PE.c |coded_country), data = dtCtry, REML = FALSE,  control = lme4::lmerControl(optimizer ="Nelder_Mead"))
  summary(mod3Rand)
  sjPlot::plot_model(mod3Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### Table: Multilevel Approach
```{r}
sjPlot::tab_model(mod1Fix, mod1Rand, mod2Fix, mod2Rand, mod3Fix, mod3Rand)
```


## Multilevel Mediation
### Simple SEM Model
```{r}
model <- '# Model 
            PE  =~ affCalm + affContent + affEnerg + affInsp + affRel 
            WB =~ happy + lifeSat + MLQ
            c19ProSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03 + c19ProSo04
          # Regression
            c19ProSo ~ a*PE
            WB ~ b*c19ProSo + c*PE'
fit <- sem(model, data = dtCtry)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### Multilevel SEM Model 1-1-1
First we run a model that has no specified level 2 (only covariances)
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
# saturated model on level 2
  model <- 'level:1
            c19ProSo.c ~ a*PE.c
            WB.m ~ b*c19ProSo.c + c*PE.c
            level:2
            c19ProSo.c ~~ PE.c
            c19ProSo.c ~~ WB.m
            WB.m ~~ PE.c
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Next we run a model that also has no level 2 specified (only intercepts)
```{r}
# level 2 only intercepts
  model <- 'level:1
            c19ProSo.c ~ a*PE.c
            WB.m ~ b*c19ProSo.c + c*PE.c
            level:2
            c19ProSo.c ~ 1
            PE.c ~1
            WB.m ~ 1
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Finally we run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
```{r}
# specified model
model <- 'level:1
          c19ProSo.c ~ a*PE.c
          WB.m ~ b*c19ProSo.c + c*PE.c
          level:2
          c19ProSo.c ~ d*PE.c
          WB.m ~ e*c19ProSo.c + f*PE.c
          # Indirect and total effects within
          ab:=a*b
          totalwith:=ab+c 
          # Indirect and total effects between
          de:=d*e
          totalbw:=de+f' 
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
lavInspect(fit, "icc")
```

##Test longitudinal
