---
title: "PsyCorona Need Threat to Compensation"
author: "PsyCorona Gang"
date: "May 2020"
output:
  html_document:
    code_folding: hide
    mathjax: default
    theme: united
    toc: yes
    toc_float: yes
    number_sections: TRUE
  pdf_document:
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
cat("\014") # clear console
rm(list=ls()) # clear workspace
gc # garbage collector

require(pacman)
p_load(metafor, dplyr, tinytex, knitr, kableExtra, DescTools, reshape2, metaSEM, lavaan, semPlot, psych, ggplot2)

set.seed(52) # set overall random seed for reproducibility
```

# Load Data
```{r LoadRawBase, echo=T, warning=F, message=F}

# Import Data
dtRaw <- haven::read_spss(dir("data/raw data", pattern = "Agostini", full.names = TRUE, ignore.case = TRUE))
```

# Prepare Data
## Cleaning
```{r clean, echo=T, warning=F, message=F}
# change all -99 into NA
  dtRaw[dtRaw == -99] <- NA

# make relevant dfs
dtFull <- dtRaw
dtCtry <- dtRaw %>% 
  group_by(coded_country) %>% # group by country
  filter(n() > 200) # remove countries with less than 100 people
dtCtry <- dtCtry %>% #needs to be ungrouped for the scale calculation
  ungroup()
rm(dtRaw)
```

## Calculate relevant variables
### Make relevant vars numeric (lavaan)
```{r makeNum, echo=F, warning=F, message=F}
# make them numeric so lavaan stops complaining
dtCtry <- dtCtry %>%
  dplyr::mutate_at(vars(matches(
    paste(c("aff", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo"), collapse = "|"), -contains("DO"))), #vars changed
    as.numeric) #function for change
```

### Scales
```{r calcVars, echo=T, warning=F, message=F}
# positive emotion
  dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel) %>% psych::describe()
  dtCtry$posEmo.m <- scoreItems(keys=c(1,1,1,1,1),
                            items = dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel) %>% na_if(., -99),
                                min = 1, max = 5)$scores
  dtCtry$posEmo.c <- scale(dtCtry$posEmo.m, scale = F, center = T)
  dtCtry$posEmo.z <- scale(dtCtry$posEmo.m, scale = T)
  dtCtry$posEmo.fa <- fa(dtCtry %>% dplyr::select(affCalm, affContent, affEnerg, affInsp, affRel))$scores

# negative emotion
  dtCtry %>% dplyr::select(affAnx, affDepr, affNerv, affExh) %>% psych::describe()
  dtCtry$negEmo.m <- scoreItems(keys=c(1,1,1,1),
                            items = dtCtry %>% dplyr::select(affAnx, affDepr, affNerv, affExh) %>% na_if(., -99),
                                min = 1, max = 5)$scores
  dtCtry$negEmo.c <- scale(dtCtry$negEmo.m, scale = F, center = T)
  dtCtry$negEmo.z <- scale(dtCtry$negEmo.m, scale = T)
  dtCtry$negEmo.fa <- fa(dtCtry %>% dplyr::select(affAnx, affDepr, affNerv, affExh))$scores

# financial strain
  dtCtry %>% dplyr::select(PFS01, PFS02, PFS03) %>% psych::describe()
  dtCtry$PFS.m <- scoreItems(keys=c(1,1,1),
                            items = dtCtry %>% dplyr::select(PFS01, PFS02, PFS03) %>% na_if(., -99),
                                min = -2, max = 2)$scores
  dtCtry$PFS.c <- scale(dtCtry$PFS.m, scale = F, center = T)
  dtCtry$PFS.z <- scale(dtCtry$PFS.m, scale = T)
  dtCtry$PFS.fa <- fa(dtCtry %>% dplyr::select(PFS01, PFS02, PFS03))$scores
  
# disempowerment
  dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% psych::describe()
  dtCtry$disemp.m <- scoreItems(keys=c(1,1,1),
                            items = dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% na_if(., -99),
                                min = -2, max = 2)$scores
  dtCtry$disemp.c <- scale(dtCtry$disemp.m, scale = F, center = T)
  dtCtry$disemp.z <- scale(dtCtry$disemp.m, scale = T)
  dtCtry$disemp.fa <- fa(dtCtry %>% dplyr::select(fail01, fail02, fail03))$scores

# Well-Being
  # need rescaling first
    dtCtry$lifeSat <- scales::rescale(as.numeric(dtCtry$lifeSat), to = c(1,10))
    dtCtry$MLQ <- scales::rescale(as.numeric(dtCtry$MLQ), to = c(1,10))
  dtCtry %>% dplyr::select(happy, lifeSat, MLQ) %>% psych::describe()
  dtCtry$WB.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(happy, lifeSat, MLQ) %>% na_if(., -99),
                                min = 1, max = 10)$scores
  dtCtry$WB.c <- scale(dtCtry$WB.m, scale = F, center = T)
  dtCtry$WB.z <- scale(dtCtry$WB.m, scale = T)
  dtCtry$WB.fa <- fa(dtCtry %>% dplyr::select(happy, lifeSat, MLQ))$scores

# pro-Social Behavior
  dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% psych::describe()
  dtCtry$c19ProSo.m <- scoreItems(keys=c(1,1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19ProSo.c <- scale(dtCtry$c19ProSo.m, scale = F, center = T)
  dtCtry$c19ProSo.z <- scale(dtCtry$c19ProSo.m, scale = T)
  dtCtry$c19ProSo.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")))$scores

```

### Interactions
```{r calcInt, echo=T, warning=F, message=F}
# calculate interactions for observed modeling
  dtCtry <- dtCtry %>%
  mutate(intPosEmoXDisemp = posEmo.c*disemp.c,
         intNegEmoXDisemp = negEmo.c*disemp.c,
         intPFSXDisemp = PFS.c*disemp.c, scale = F, center = T)
```


# Analysis
## Confirmatory Factor Analysis
```{r explrFactor12}
  model <- 'level:1
            # Latent
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel 
            negEmo =~ affAnx + affDepr + affNerv + affExh
            PFS =~ PFS01 + PFS02 + PFS03
            disemp =~ fail01 + fail02 + fail03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            level:2
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel
            negEmo =~ affAnx + affDepr + affNerv + affExh
            disemp =~ fail01 + fail02 + fail03
            PFS =~ PFS01 + PFS02 + PFS03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03'
#fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

<!-- ### MultiGroup Confirmatory Factor Analysis -->
<!-- ```{r explrFactor} -->
<!-- # by country all -->
<!--   fitGroup <- cfa(model, data = dtCtry, group = "coded_country") -->
<!--   summary(fitGroup, fit.measures=TRUE) -->

<!-- # by country constrained -->
<!--   #fitGroupConstr <- sem(model, dtCtry, group = "coded_country", group.equal = c("intercepts", "regressions")) -->

<!-- # compare unconstrained and constrained -->
<!--   #anova(fitGroup, fitGroupConstr) -->
<!-- ``` -->

## MultiLevel Approach
### posEmo - Well-Being with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = posEmo.m, y = WB.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod1Fix <- lme4::lmer(WB.m ~ posEmo.c + (1|coded_country), data = dtCtry)
  summary(mod1Fix)
```

### posEmo - Well-Being with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = posEmo.m, y = WB.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod1Rand <- lme4::lmer(WB.m ~ posEmo.c + (1 + posEmo.c|coded_country), data = dtCtry)
  anova(mod1Fix, mod1Rand) # test diff
  summary(mod1Rand)
  sjPlot::plot_model(mod1Rand, type = c("re"), show.values = T, value.offset = .5)

```

### Pro-Social - Well-Being with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod2Fix <- lme4::lmer(WB.m ~ c19ProSo.c + (1|coded_country), data = dtCtry)
  summary(mod2Fix)
```

### ProSo - Well-Being with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod2Rand <- lme4::lmer(WB.m ~ c19ProSo.c + (1 + c19ProSo.c|coded_country), data = dtCtry)
  anova(mod2Fix, mod2Rand) # test diff
  summary(mod2Rand)
  sjPlot::plot_model(mod2Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### posEmo -ProSo - Well-Being with Fixed Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# plotly::ggplotly(tmp)

# fit model with random slope
  mod3Fix <- lme4::lmer(WB.m ~ c19ProSo.c + posEmo.c + (1|coded_country), data = dtCtry)
  summary(mod3Fix)
  sjPlot::plot_model(mod3Fix, type =  c("re"), show.values = T, value.offset = .5)
```

### posEmo -ProSo - Well-Being with Random Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = c19ProSo.m, y = WB.m, color = coded_country)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# plotly::ggplotly(tmp)

# fit model with random slope
  mod3Rand <- lme4::lmer(WB.m ~ c19ProSo.c + posEmo.c + (1+ c19ProSo.c + posEmo.c |coded_country), data = dtCtry, REML = FALSE,  control = lme4::lmerControl(optimizer ="Nelder_Mead"))
  summary(mod3Rand)
  sjPlot::plot_model(mod3Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### DV: Well-Being full model
```{r}
# fit model with random slope
  mod5Med <- lme4::lmer(WB.z ~ disemp.z*posEmo.z + disemp.z*negEmo.z + disemp.z*PFS.z + (1 |coded_country), data = dtCtry)
  mod5DV <- lme4::lmer(c19ProSo.m ~ WB.z + disemp.z*posEmo.z + disemp.z*negEmo.z + disemp.z*PFS.z + (1 |coded_country), data = dtCtry)
  summary(mod5Med)
  summary(mod5DV)
# mediation  
  anaMed <- mediation::mediate(mod5Med, mod5DV, treat='negEmo.z', mediator='WB.z', sims = 100)
  summary(anaMed)
# test for moderated mediation
  mediation::test.modmed(anaMed, list(disemp.z = -1), covariates.2 = list(disemp.z = 1), sims = 100)

# test for values at different levels of moderator 
  
  
  
  lattice::dotplot(ranef(mod5Rand, postVar=TRUE))
  
  

```

### Table: Multilevel Approach
```{r}
sjPlot::tab_model(mod1Fix, mod1Rand, mod2Fix, mod2Rand, mod3Fix, mod3Rand)
```


## Multilevel Path Modeling
### CFA: Check latent constructs
```{r}
  model <- 'level:1
            # Latent
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel 
            negEmo =~ affAnx + affDepr + affNerv + affExh
            PFS =~ PFS01 + PFS02 + PFS03
            disemp =~ fail01 + fail02 + fail03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            level:2
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel
            negEmo =~ affAnx + affDepr + affNerv + affExh
            disemp =~ fail01 + fail02 + fail03
            PFS =~ PFS01 + PFS02 + PFS03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03'
#fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)

```

### Well-Being as DV
We run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
  model <- 'level:1
            # a path
            WB.m ~ a1*posEmo.c + a2*negEmo.c + a3*PFS.c + a4*disemp.c + a5*intPosEmoXDisemp + a6*intNegEmoXDisemp + a7*intPFSXDisemp
            level:2
            # d path
            WB.m ~ d1*posEmo.c + d2*negEmo.c + d3*PFS.c + d4*disemp.c + d5*intPosEmoXDisemp + d6*intNegEmoXDisemp + d7*intPFSXDisemp'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
# fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
#            em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavInspect(fit, "icc")
```

### Pro-Sociality as DV
We run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
  model <- 'level:1
            # c path
            c19ProSo.m ~ c1*posEmo.c + c2*negEmo.c + c3*PFS.c + c4*disemp.c + c5*intPosEmoXDisemp + c6*intNegEmoXDisemp + c7*intPFSXDisemp
            # a path
            WB.m ~ a1*posEmo.c + a2*negEmo.c + a3*PFS.c + a4*disemp.c + a5*intPosEmoXDisemp + a6*intNegEmoXDisemp + a7*intPFSXDisemp
            # b path
            c19ProSo.m ~ b1*WB.m
            level:2
            # f path
            c19ProSo.m ~ f1*posEmo.c + f2*negEmo.c + f3*PFS.c + f4*disemp.c + f5*intPosEmoXDisemp + f6*intNegEmoXDisemp + f7*intPFSXDisemp
            # d path
            WB.m ~ d1*posEmo.c + d2*negEmo.c + d3*PFS.c + d4*disemp.c + d5*intPosEmoXDisemp + d6*intNegEmoXDisemp + d7*intPFSXDisemp
            # e path
            c19ProSo.m ~ e1*WB.m'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
# fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
#            em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavInspect(fit, "icc")
```

# OLD CODE: THIS IS REALLY COOL BUT DOES NOT WORK VERY WELL
## Multilevel SEM
### Mean Center all relevant vars
```{r}
# mean center the individual scales (this works but want to be sure)
  # dtCtry <- dtCtry %>%
  #   dplyr::mutate_at(vars(matches(
  #     paste(c("aff", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo"), collapse = "|"), -contains("DO"))), #vars changed
  #     scale, center = T, scale = F) #function for change


# mean center "save" way
dtCtry <- dtCtry %>%
    mutate(affCalm = scale(affCalm, center = T, scale = F),
           affContent = scale(affContent, center = T, scale = F),
           affEnerg = scale(affEnerg, center = T, scale = F),
           affInsp = scale(affInsp, center = T, scale = F),
           affRel = scale(affRel, center = T, scale = F),
           affAnx = scale(affAnx, center = T, scale = F),
           affDepr = scale(affDepr, center = T, scale = F),
           affNerv = scale(affNerv, center = T, scale = F),
           affExh = scale(affExh, center = T, scale = F),
           PFS01 = scale(PFS01, center = T, scale = F),
           PFS02 = scale(PFS02, center = T, scale = F),
           PFS03 = scale(PFS03, center = T, scale = F),
           fail01 = scale(fail01, center = T, scale = F),
           fail02 = scale(fail02, center = T, scale = F),
           fail03 = scale(fail03, center = T, scale = F),
           happy = scale(happy, center = T, scale = F),
           lifeSat = scale(lifeSat, center = T, scale = F),
           MLQ = scale(MLQ, center = T, scale = F),
           c19ProSo01 = scale(c19ProSo01, center = T, scale = F),
           c19ProSo02 = scale(c19ProSo02, center = T, scale = F),
           c19ProSo03 = scale(c19ProSo03, center = T, scale = F),
           c19ProSo04 = scale(c19ProSo04, center = T, scale = F),
           )


# calculate interactions for the latent constructs
  dtCtry <- dtCtry %>%
    mutate(fail01XposEmo01 = scale(fail01*affCalm, center = T, scale = F),
           fail01XposEmo02 = scale(fail01*affContent, center = T, scale = F),
           fail01XposEmo03 = scale(fail01*affEnerg, center = T, scale = F),
           fail01XposEmo04 = scale(fail01*affInsp, center = T, scale = F),
           fail01XposEmo05 = scale(fail01*affRel, center = T, scale = F),
           fail02XposEmo01 = scale(fail02*affCalm, center = T, scale = F),
           fail02XposEmo02 = scale(fail02*affContent, center = T, scale = F),
           fail02XposEmo03 = scale(fail02*affEnerg, center = T, scale = F),
           fail02XposEmo04 = scale(fail02*affInsp, center = T, scale = F),
           fail02XposEmo05 = scale(fail02*affRel, center = T, scale = F),
           fail03XposEmo01 = scale(fail03*affCalm, center = T, scale = F),
           fail03XposEmo02 = scale(fail03*affContent, center = T, scale = F),
           fail03XposEmo03 = scale(fail03*affEnerg, center = T, scale = F),
           fail03XposEmo04 = scale(fail03*affInsp, center = T, scale = F),
           fail03XposEmo05 = scale(fail03*affRel, center = T, scale = F)
           )

  # calculate interactions for the latent constructs
  dtCtry <- dtCtry %>%
    mutate(fail01XposEmo01 = fail01*affCalm,
           fail01XposEmo02 = fail01*affContent,
           fail01XposEmo03 = fail01*affEnerg,
           fail01XposEmo04 = fail01*affInsp,
           fail01XposEmo05 = fail01*affRel,
           fail02XposEmo01 = fail02*affCalm,
           fail02XposEmo02 = fail02*affContent,
           fail02XposEmo03 = fail02*affEnerg,
           fail02XposEmo04 = fail02*affInsp,
           fail02XposEmo05 = fail02*affRel,
           fail03XposEmo01 = fail03*affCalm,
           fail03XposEmo02 = fail03*affContent,
           fail03XposEmo03 = fail03*affEnerg,
           fail03XposEmo04 = fail03*affInsp,
           fail03XposEmo05 = fail03*affRel
           )
```


### posEmo - WB - proSo 
#### Normal SEM
```{r}
model <- '# Model 
            posEmo  =~ affCalm + affContent + affEnerg + affInsp + affRel 
            WB =~ happy + lifeSat + MLQ
            c19ProSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03 + c19ProSo04
          # Regression
            c19ProSo ~ a*posEmo
            WB ~ b*c19ProSo + c*posEmo'
fit <- sem(model, data = dtCtry)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)


```

#### Multilevel SEM Model 1-1-1
First we run a model that has no specified level 2 (only covariances)
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
# saturated model on level 2
  model <- 'level:1
            c19ProSo.c ~ a*posEmo.c
            WB.m ~ b*c19ProSo.c + c*posEmo.c
            level:2
            c19ProSo.c ~~ posEmo.c
            c19ProSo.c ~~ WB.m
            WB.m ~~ posEmo.c
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Next we run a model that also has no level 2 specified (only intercepts)
```{r}
# level 2 only intercepts
  model <- 'level:1
            c19ProSo.c ~ a*posEmo.c
            WB.m ~ b*c19ProSo.c + c*posEmo.c
            level:2
            c19ProSo.c ~ 1
            posEmo.c ~1
            WB.m ~ 1
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Finally we run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
```{r}
# specified model
model <- 'level:1
          c19ProSo.c ~ a*posEmo.c
          WB.m ~ b*c19ProSo.c + c*posEmo.c
          level:2
          c19ProSo.c ~ d*posEmo.c
          WB.m ~ e*c19ProSo.c + f*posEmo.c
          # Indirect and total effects within
          ab:=a*b
          totalwith:=ab+c 
          # Indirect and total effects between
          de:=d*e
          totalbw:=de+f' 
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
lavInspect(fit, "icc")
```

### predictors - WB  
#### Multilevel SEM (latent vars)
##### First: Measurement model
We run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
In this first step, we test the measurement model to see whether the constructs even fit. Fit indeces seem adequate.
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
  model <- 'level:1
            # Latent
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel 
            negEmo =~ affAnx + affDepr + affNerv + affExh
            PFS =~ PFS01 + PFS02 + PFS03
            disemp =~ fail01 + fail02 + fail03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            level:2
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel
            negEmo =~ affAnx + affDepr + affNerv + affExh
            disemp =~ fail01 + fail02 + fail03
            PFS =~ PFS01 + PFS02 + PFS03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000, em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)

```

##### Second: Regression Model
```{r}
  model <- 'level:1
          # Latent IVs
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel 
            negEmo =~ affAnx + affDepr + affNerv + affExh
            PFS =~ PFS01 + PFS02 + PFS03
            disemp =~ fail01 + fail02 + fail03
          # Latent Mediator
            wellBe =~ happy + lifeSat + MLQ
          # Latent DV
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          # Regression
            wellBe ~ a1*posEmo + a2*negEmo + a3*PFS + a4*disemp
            level:2
          # Latent
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel
            negEmo =~ affAnx + affDepr + affNerv + affExh
            disemp =~ fail01 + fail02 + fail03
            PFS =~ PFS01 + PFS02 + PFS03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          # Regression
            wellBe ~ d1*posEmo + d2*negEmo + d3*PFS + d4*disemp'
#fit <- sem(model, data = dtCtry, cluster = "coded_country")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

##### Third: Interaction Model
```{r}
  model <- 'level:1
          # Latent Constructs
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel 
            negEmo =~ affAnx + affDepr + affNerv + affExh
            PFS =~ PFS01 + PFS02 + PFS03
            disemp =~ fail01 + fail02 + fail03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          # Interactions
            failXposEmo =~ fail01XposEmo01 + fail01XposEmo02 + fail01XposEmo03 + fail01XposEmo04 + fail01XposEmo05 + fail02XposEmo01 + fail02XposEmo02 + fail02XposEmo03 + fail02XposEmo04 + fail02XposEmo05 + fail03XposEmo01 + fail03XposEmo02 + fail03XposEmo03 + fail03XposEmo04 + fail03XposEmo05
          # Regression
            wellBe ~ a1*posEmo + a2*negEmo + a3*PFS + a4*disemp + a5*failXposEmo
            level:2
          # Latent Constructs
            posEmo =~ affCalm + affContent + affEnerg + affInsp + affRel
            negEmo =~ affAnx + affDepr + affNerv + affExh
            disemp =~ fail01 + fail02 + fail03
            PFS =~ PFS01 + PFS02 + PFS03
            wellBe =~ happy + lifeSat + MLQ
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          # Interactions
            failXposEmo =~ fail01XposEmo01 + fail01XposEmo02 + fail01XposEmo03 + fail01XposEmo04 + fail01XposEmo05 + fail02XposEmo01 + fail02XposEmo02 + fail02XposEmo03 + fail02XposEmo04 + fail02XposEmo05 + fail03XposEmo01 + fail03XposEmo02 + fail03XposEmo03 + fail03XposEmo04 + fail03XposEmo05
          # Regression
            wellBe ~ d1*posEmo + d2*negEmo + d3*PFS + d4*disemp + d6*failXposEmo'

fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000, em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
 lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
 
# semTools::plotProbe (probe a latent interaction) https://rdrr.io/cran/semTools/man/plotProbe.html
 
```

## Longitudinal
```{r}

# use growth() from lavaan package with cluster
```

