---
title: "PsyCorona Need Threat to Compensation"
author: "Maximilian Agostini"
date: "May 2020"
output:
  html_document:
    code_folding: hide
    mathjax: default
    theme: united
    toc: yes
    toc_float: yes
    number_sections: TRUE
  pdf_document:
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
cat("\014") # clear console
rm(list=ls()) # clear workspace
gc # garbage collector

require(pacman)
p_load(metafor, dplyr, tinytex, knitr, kableExtra, DescTools, reshape2, metaSEM, lavaan, semPlot, psych, ggplot2)

set.seed(52) # set overall random seed for reproducibility
```

# Load Data
```{r LoadRawBase, echo=T, warning=F, message=F}

# Import Data
dtRaw <- haven::read_spss(dir("data/raw data", pattern = "Agostini", full.names = TRUE, ignore.case = TRUE))
```

# Prepare Data
## Cleaning
```{r clean, echo=T, warning=F, message=F}
# change all -99 into NA
  dtRaw[dtRaw == -99] <- NA

# make relevant dfs
dtFull <- dtRaw
dtCtry <- dtRaw %>% 
  group_by(coded_country) %>% # group by country
  filter(n() > 200) # remove countries with less than 100 people
dtCtry <- dtCtry %>% #needs to be ungrouped for the scale calculation
  ungroup()
rm(dtRaw)
```


## Calculate relevant variables
### Make relevant vars numeric (lavaan)
```{r makeNum, echo=F, warning=F, message=F}
# make them numeric so lavaan stops complaining
dtCtry <- dtCtry %>%
  dplyr::mutate_at(vars(matches(
    paste(c("aff", "disc", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo", "para", "consp", "c19perBeh", "c19RCA", "csqC19Contract", "c19Is"), 
          collapse = "|"), -contains("DO"))), #vars changed
    as.numeric) #function for change

```

### Scales
```{r calcVars, echo=T, warning=F, message=F}
# disempowerment
  dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% psych::describe()
  dtCtry$disemp.m <- scoreItems(keys=c(1,1,1),
                            items = dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% na_if(., -99),
                                min = -2, max = 2)$scores
  dtCtry$disemp.c <- scale(dtCtry$disemp.m, scale = F, center = T)
  dtCtry$disemp.z <- scale(dtCtry$disemp.m, scale = T)
  dtCtry$disemp.fa <- fa(dtCtry %>% dplyr::select(fail01, fail02, fail03))$scores

# discontent
  dtCtry %>% dplyr::select(disc01, disc02, disc03) %>% psych::describe()
  dtCtry$disc.m <- scoreItems(keys=c(1,1,1),
                            items = dtCtry %>% dplyr::select(disc01, disc02, disc03) %>% na_if(., -99),
                                min = -2, max = 2)$scores
  dtCtry$disc.c <- scale(dtCtry$disc.m, scale = F, center = T)
  dtCtry$disc.z <- scale(dtCtry$disc.m, scale = T)
  dtCtry$disc.fa <- fa(dtCtry %>% dplyr::select(disc01, disc02, disc03))$scores

# Paranoia
  dtCtry %>% dplyr::select(para01, para02, para03) %>% psych::describe()
  dtCtry$para.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(para01, para02, para03) %>% na_if(., -99),
                                min = 0, max = 10)$scores
  dtCtry$para.c <- scale(dtCtry$para.m, scale = F, center = T)
  dtCtry$para.z <- scale(dtCtry$para.m, scale = T)
  dtCtry$para.fa <- fa(dtCtry %>% dplyr::select(para01, para02, para03))$scores

# Conspiracy (they only use two items)
  dtCtry %>% dplyr::select(consp01, consp02, consp03) %>% psych::describe()
  dtCtry$consp.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(consp01, consp02, consp03) %>% na_if(., -99),
                                min = 0, max = 10)$scores
  dtCtry$consp.c <- scale(dtCtry$consp.m, scale = F, center = T)
  dtCtry$consp.z <- scale(dtCtry$consp.m, scale = T)
  dtCtry$consp.fa <- fa(dtCtry %>% dplyr::select(consp01, consp02, consp03))$scores

# Restriction
  dtCtry %>% dplyr::select(c19IsStrict, c19IsPunish, c19IsOrg) %>% psych::describe()
  dtCtry$restr.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(c19IsStrict, c19IsPunish, c19IsOrg) %>% na_if(., -99),
                                min = 1, max = 6)$scores
  dtCtry$restr.c <- scale(dtCtry$restr.m, scale = F, center = T)
  dtCtry$restr.z <- scale(dtCtry$restr.m, scale = T)
  dtCtry$restr.fa <- fa(dtCtry %>% dplyr::select(c19IsStrict, c19IsPunish, c19IsOrg))$scores  
  
# c19 Pro-Social Behavior
  dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% psych::describe()
  dtCtry$c19ProSo.m <- scoreItems(keys=c(1,1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19ProSo.c <- scale(dtCtry$c19ProSo.m, scale = F, center = T)
  dtCtry$c19ProSo.z <- scale(dtCtry$c19ProSo.m, scale = T)
  dtCtry$c19ProSo.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")))$scores

# c19 Self-Serving Behavior
  dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")) %>% psych::describe()
  dtCtry$c19perBeh.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19perBeh.c <- scale(dtCtry$c19perBeh.m, scale = F, center = T)
  dtCtry$c19perBeh.z <- scale(dtCtry$c19perBeh.m, scale = T)
  dtCtry$c19perBeh.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")))$scores

# c19 Radical Behavior
  dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")) %>% psych::describe()
  dtCtry$c19RCA.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19RCA.c <- scale(dtCtry$c19RCA.m, scale = F, center = T)
  dtCtry$c19RCA.z <- scale(dtCtry$c19RCA.m, scale = T)
  dtCtry$c19RCA.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")))$scores

# financial Threat
  dtCtry %>% dplyr::select(csqEcoSuffer, PFS01, PFS02, PFS03, PLRAEco) %>% psych::describe()
  # rescale first
    dtCtry$PFS01 <- scales::rescale(as.numeric(dtCtry$PFS01), to = c(1,5))
    dtCtry$PFS02 <- scales::rescale(as.numeric(dtCtry$PFS02), to = c(1,5))
    dtCtry$PFS03 <- scales::rescale(as.numeric(dtCtry$PFS03), to = c(1,5))
    dtCtry$PLRAEco <- scales::rescale(as.numeric(dtCtry$PLRAEco), to = c(1,5))
    dtCtry %>% dplyr::select(csqEcoSuffer, PFS01, PFS02, PFS03, PLRAEco) %>% psych::describe()
  dtCtry$finThr.m <- scoreItems(keys=c(1,1,1,1,1),
                                items = dtCtry %>% dplyr::select(csqEcoSuffer, PFS01, PFS02, PFS03, PLRAEco) %>% na_if(., -99),
                                min = 1, max = 5)$scores
  dtCtry$finThr.c <- scale(dtCtry$finThr.m, scale = F, center = T)
  dtCtry$finThr.z <- scale(dtCtry$finThr.m, scale = T)
  dtCtry$finThr.fa <- fa(dtCtry %>% dplyr::select(csqEcoSuffer, PFS01, PFS02, PFS03, PLRAEco))$scores
  
# physical Threat
  psych::describe(dtCtry$csqC19Contract)
  dtCtry$perThr.m <- scoreItems(keys=c(1),
                                items = dtCtry %>% dplyr::select(csqC19Contract) %>% na_if(., -99),
                                min = 1, max = 5)$scores
  dtCtry$perThr.c <- scale(dtCtry$perThr.m, scale = F, center = T)
  dtCtry$perThr.z <- scale(dtCtry$perThr.m, scale = T)
  dtCtry$perThr.fa <- fa(dtCtry %>% dplyr::select(csqC19Contract))$scores

```

# Analysis
## MultLevel Regressions
### finThreat - Discontent
#### fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = disc.m, y = consp.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod1Fix <- lme4::lmer(consp.m ~ disc.m + (1|coded_country), data = dtCtry)
  summary(mod1Fix)
```

#### random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = disc.m, y = consp.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod1Rand <- lme4::lmer(consp.m ~ disc.m + (1 + disemp.c|coded_country), data = dtCtry)
  anova(mod1Fix, mod1Rand) # test diff
  summary(mod1Rand)
  lattice::dotplot(ranef(mod1Rand, postVar=TRUE))
```

### finThreat - Conspiracy
#### fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = finThr.m, y = consp.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod1Fix <- lme4::lmer(consp.m ~ finThr.m + (1|coded_country), data = dtCtry)
  summary(mod1Fix)
```

#### random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = finThr.m, y = consp.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod1Rand <- lme4::lmer(consp.m ~ finThr.m + (1 + disemp.c|coded_country), data = dtCtry)
  anova(mod1Fix, mod1Rand) # test diff
  summary(mod1Rand)
  lattice::dotplot(ranef(mod1Rand, postVar=TRUE))
```

### Table: Multilevel Approach
```{r}
#sjPlot::tab_model(mod1Fix, mod1Rand, mod2Fix, mod2Rand, mod3Fix, mod3Rand)
```

## Causal Multilevel Mediation
### finThreat - disc - consp
#### fixed slope
```{r}
# fit model with fixed slope
  modMed <- lme4::lmer(disc.z ~ finThr.z + (1|coded_country), data = dtCtry)
  modDV <- lme4::lmer(c19ProSo.m ~ disc.z + finThr.z + (1|coded_country), data = dtCtry)
  summary(modMed)
  summary(modDV)
# mediation  
  anaMed <- mediation::mediate(modMed, modDV, treat='finThr.z', mediator='disc.z', sims = 100)
   summary(anaMed)
# test for moderated mediation
```

#### random slope
```{r}
# fit model with fixed slope
  modMed <- lme4::lmer(disc.z ~ finThr.z + (finThr.z|coded_country), data = dtCtry)
  modDV <- lme4::lmer(c19ProSo.m ~ disc.z + finThr.z + (finThr.z|coded_country), data = dtCtry)
  summary(modMed)
  summary(modDV)
# mediation  
  anaMed <- mediation::mediate(modMed, modDV, treat='finThr.z', mediator='disc.z', sims = 100)
   summary(anaMed)
# test for moderated mediation
```

## ML Mediation (mediate) DOES NOT WORK
```{r}
# fit model with random slope
  # models for the moderated mediation test
    modMedInit <- lme4::lmer(disc.z ~ finThr.z + disemp.z + (finThr.z|coded_country), data = dtCtry)
    modDVInit <- lme4::lmer(c19ProSo.m ~ finThr.z + disc.z + disemp.z + (finThr.z|coded_country), data = dtCtry)
  # models for testing the effect at different values of the moderator
    modMed <- lme4::lmer(disc.z ~ finThr.z*disemp.z + (finThr.z|coded_country), data = dtCtry)
    modDV <- lme4::lmer(c19ProSo.m ~ finThr.z + disc.z*disemp.z + (finThr.z|coded_country), data = dtCtry)
  #modDV <- lmerTest::lmer(c19ProSo.m ~ finThr.z + disc.z*disemp.z + (finThr.z|coded_country), data = dtCtry)
  summary(modMed)
  summary(modDV)
# mediation 
  medInit <- mediation::mediate(modMedInit, modDVInit, treat = "finThr.z", mediator = "disc.z", sims = 100)
  summary(medInit)
  medDisempLow <- mediation::mediate(modMed, modDV, treat = "finThr.z", mediator = "disc.z", covariates = list(disemp.z = -1), sims = 100)
  medDisempHigh <- mediation::mediate(modMed, modDV, treat = "finThr.z", mediator = "disc.z", covariates = list(disemp.z = 1), sims = 100)
  
 # mediation::test.modmed(medInit, covariates.1 = list(disemp.z = -1), covariates.2 = list(disemp.z = 1), sims = 100)

   summary(medDisempLow)
   summary(medDisempHigh)
# test for moderated mediation
```


## Multilevel Moderated Mediation (lavaan)
### Simple Mediation
check here: https://nmmichalak.github.io/nicholas_michalak/blog_entries/2018/nrg02/nrg02.html
https://nickmichalak.com/post/2019-02-14-testing-conditional-indirect-effects-mediation-in-r/testing-conditional-indirect-effects-mediation-in-r/
https://stats.stackexchange.com/questions/163436/r-moderated-mediation-using-the-lavaan-package
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            # Regression
            consp ~ a1*disemp
            perBeh ~ b1*consp + c1*disemp
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            # Regression
            consp ~ d1*disemp
            perBeh ~ e1*consp + f1*disemp
            # Indirect and total effects within
            ab:=a1*b1
            totalwith:=ab+c1
            # Indirect and total effects between
            de:=d1*e1
            totalbw:=de+f1'



```

## Three-Way Interaction Multilevel
```{r}

# fit model with fixed slope
  modFix <- lme4::lmer(consp.m ~ finThr.z*disemp.z*para.z + (1|coded_country), data = dtCtry)
  summary(modFix)
  modRand1 <- lme4::lmer(consp.m ~ finThr.z*disemp.z*para.z + (finThr.z|coded_country), data = dtCtry)
  #anova(modRand1, modFix)
  summary(modRand1) # for both paranoia and finanical Threat no convergence
  
  t = summary(modRand1) %>% # get the model summary
    coef() %>% # get the coefficients from the model summary
    round(digits = 3) %>% # round the coefficients to two digits
    data.frame()
  t$upci = t$Estimate+1.96*t$Std..Error
  t$lowci = t$Estimate-1.96*t$Std..Error
  t; rm(t)
  
  # tmp <- interactions::sim_slopes(modRand1, pred = finThr.z, 
  #            modx = disemp.z,
  #            mod2 = para.z,
  #            jnplot = TRUE) 
  # tmp
  

```




<!-- # OLD CODE -->
<!-- ## Multilevel Mediation -->
<!-- ### Simple SEM Model -->
<!-- ```{r} -->
<!-- model <- '# Model  -->
<!--             disemp  =~ affCalm + affContent + affEnerg + affInsp + affRel  -->
<!--             consp =~ happy + lifeSat + MLQ -->
<!--             para =~ para01 + para02 + para03 -->
<!--           # Regression -->
<!--             para ~ a*disemp -->
<!--             consp ~ b*para + c*disemp' -->
<!-- fit <- sem(model, data = dtCtry) -->
<!-- summary(fit, fit.measures=TRUE) -->
<!-- lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T) -->
<!-- ``` -->

<!-- ### Multilevel SEM Model 1-1-1 -->
<!-- First we run a model that has no specified level 2 (only covariances) -->
<!-- ```{r} -->
<!-- # Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY): -->
<!-- # By adding the same model again on level 2, we are estimating the latent means now -->
<!-- # saturated model on level 2 -->
<!--   model <- 'level:1 -->
<!--             para.c ~ a*disemp.c -->
<!--             consp.m ~ b*para.c + c*disemp.c -->
<!--             level:2 -->
<!--             para.c ~~ disemp.c -->
<!--             para.c ~~ consp.m -->
<!--             consp.m ~~ disemp.c -->
<!--             # Indirect effects -->
<!--             ab:=a*b -->
<!--             total:=ab+c' -->
<!-- fit <- sem(model, data = dtCtry, cluster = "coded_country") -->
<!-- summary(fit, fit.measures=TRUE) -->
<!-- ``` -->

<!-- Next we run a model that also has no level 2 specified (only intercepts) -->
<!-- ```{r} -->
<!-- # level 2 only intercepts -->
<!--   model <- 'level:1 -->
<!--             para.c ~ a*disemp.c -->
<!--             consp.m ~ b*para.c + c*disemp.c -->
<!--             level:2 -->
<!--             para.c ~ 1 -->
<!--             disemp.c ~1 -->
<!--             consp.m ~ 1 -->
<!--             # Indirect effects -->
<!--             ab:=a*b -->
<!--             total:=ab+c' -->
<!-- fit <- sem(model, data = dtCtry, cluster = "coded_country") -->
<!-- summary(fit, fit.measures=TRUE) -->
<!-- ``` -->

<!-- Finally we run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values. -->
<!-- ```{r} -->
<!-- # specified model -->
<!-- model <- 'level:1 -->
<!--           para.c ~ a*disemp.c -->
<!--           consp.m ~ b*para.c + c*disemp.c -->
<!--           level:2 -->
<!--           para.c ~ d*disemp.c -->
<!--           consp.m ~ e*para.c + f*disemp.c -->
<!--           # Indirect and total effects within -->
<!--           ab:=a*b -->
<!--           totalwith:=ab+c  -->
<!--           # Indirect and total effects between -->
<!--           de:=d*e -->
<!--           totalbw:=de+f'  -->
<!-- fit <- sem(model, data = dtCtry, cluster = "coded_country") -->
<!-- summary(fit, fit.measures=TRUE) -->
<!-- lavInspect(fit, "icc") -->
<!-- ``` -->

<!-- ##Test longitudinal -->
