---
title: "PsyCorona Need Threat to Compensation"
author: "Maximilian Agostini, Anton Martinez"
date: "May 2020"
output:
  html_document:
    code_folding: hide
    mathjax: default
    theme: united
    toc: yes
    toc_float: yes
    number_sections: TRUE
  pdf_document:
    toc: yes
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
cat("\014") # clear console
rm(list=ls()) # clear workspace
gc # garbage collector

require(pacman)
p_load(metafor, dplyr, tinytex, knitr, kableExtra, DescTools, reshape2, metaSEM, lavaan, semPlot, psych, ggplot2)

set.seed(52) # set overall random seed for reproducibility
```

# Load Data
```{r LoadRawBase, echo=T, warning=F, message=F}

# Import Data
dtRaw <- haven::read_spss(dir("data/raw data", pattern = "Agostini", full.names = TRUE, ignore.case = TRUE))
```

# Prepare Data
## Cleaning
```{r clean, echo=T, warning=F, message=F}
# change all -99 into NA
  dtRaw[dtRaw == -99] <- NA

# make relevant dfs
dtFull <- dtRaw
dtCtry <- dtRaw %>% 
  group_by(coded_country) %>% # group by country
  filter(n() > 200) # remove countries with less than 100 people
dtCtry <- dtCtry %>% #needs to be ungrouped for the scale calculation
  ungroup()
rm(dtRaw)
```


## Calculate relevant variables
### Make relevant vars numeric (lavaan)
```{r makeNum, echo=F, warning=F, message=F}
# make them numeric so lavaan stops complaining
dtCtry <- dtCtry %>%
  dplyr::mutate_at(vars(matches(
    paste(c("aff", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo", "para", "consp", "c19perBeh", "c19RCA"), 
          collapse = "|"), -contains("DO"))), #vars changed
    as.numeric) #function for change

```

### Scales
```{r calcVars, echo=T, warning=F, message=F}
# disempowerment
  dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% psych::describe()
  dtCtry$disemp.m <- scoreItems(keys=c(1,1,1),
                            items = dtCtry %>% dplyr::select(fail01, fail02, fail03) %>% na_if(., -99),
                                min = -2, max = 2)$scores
  dtCtry$disemp.c <- scale(dtCtry$disemp.m, scale = F, center = T)
  dtCtry$disemp.z <- scale(dtCtry$disemp.m, scale = T)
  dtCtry$disemp.fa <- fa(dtCtry %>% dplyr::select(fail01, fail02, fail03))$scores

# Paranoia
  dtCtry %>% dplyr::select(para01, para02, para03) %>% psych::describe()
  dtCtry$para.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(para01, para02, para03) %>% na_if(., -99),
                                min = 0, max = 10)$scores
  dtCtry$para.c <- scale(dtCtry$para.m, scale = F, center = T)
  dtCtry$para.z <- scale(dtCtry$para.m, scale = T)
  dtCtry$para.fa <- fa(dtCtry %>% dplyr::select(para01, para02, para03))$scores

# Conspiracy
  dtCtry %>% dplyr::select(consp01, consp02, consp03) %>% psych::describe()
  dtCtry$consp.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(consp01, consp02, consp03) %>% na_if(., -99),
                                min = 0, max = 10)$scores
  dtCtry$consp.c <- scale(dtCtry$consp.m, scale = F, center = T)
  dtCtry$consp.z <- scale(dtCtry$consp.m, scale = T)
  dtCtry$consp.fa <- fa(dtCtry %>% dplyr::select(consp01, consp02, consp03))$scores
  
# c19 Pro-Social Behavior
  dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% psych::describe()
  dtCtry$c19ProSo.m <- scoreItems(keys=c(1,1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19ProSo.c <- scale(dtCtry$c19ProSo.m, scale = F, center = T)
  dtCtry$c19ProSo.z <- scale(dtCtry$c19ProSo.m, scale = T)
  dtCtry$c19ProSo.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19ProSo"), -contains("DO")))$scores

# c19 Self-Serving Behavior
  dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")) %>% psych::describe()
  dtCtry$c19perBeh.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19perBeh.c <- scale(dtCtry$c19perBeh.m, scale = F, center = T)
  dtCtry$c19perBeh.z <- scale(dtCtry$c19perBeh.m, scale = T)
  dtCtry$c19perBeh.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19perBeh"), -contains("DO")))$scores

# c19 Radical Behavior
  dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")) %>% psych::describe()
  dtCtry$c19RCA.m <- scoreItems(keys=c(1,1,1),
                                items = dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")) %>% na_if(., -99),
                                min = -3, max = 3)$scores
  dtCtry$c19RCA.c <- scale(dtCtry$c19RCA.m, scale = F, center = T)
  dtCtry$c19RCA.z <- scale(dtCtry$c19RCA.m, scale = T)
  dtCtry$c19RCA.fa <- fa(dtCtry %>% dplyr::select(starts_with("c19RCA"), -contains("DO")))$scores

```

# Methods
We collected a total of `r nrow(dtCtry)` from `r nrow(table(dtCtry$coded_country))` countries. We excluded 
```{r}
# number participants
  nrow(dtCtry)
# number countries
  nrow(table(dtCtry$coded_country))
# participants excluded
  nrow(dtFull)-nrow(dtCtry)

```

### Mean Center all relevant vars
```{r}
# mean center the individual scales (this works but want to be sure)
  # dtCtry <- dtCtry %>%
  #   dplyr::mutate_at(vars(matches(
  #     paste(c("aff", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo"), collapse = "|"), -contains("DO"))), #vars changed
  #     scale, center = T, scale = F) #function for change


# mean center "save" way
dtCtry <- dtCtry %>%
    mutate(affCalm = scale(affCalm, center = T, scale = F),
           affContent = scale(affContent, center = T, scale = F),
           affEnerg = scale(affEnerg, center = T, scale = F),
           affInsp = scale(affInsp, center = T, scale = F),
           affRel = scale(affRel, center = T, scale = F),
           affAnx = scale(affAnx, center = T, scale = F),
           affDepr = scale(affDepr, center = T, scale = F),
           affNerv = scale(affNerv, center = T, scale = F),
           affExh = scale(affExh, center = T, scale = F),
           PFS01 = scale(PFS01, center = T, scale = F),
           PFS02 = scale(PFS02, center = T, scale = F),
           PFS03 = scale(PFS03, center = T, scale = F),
           fail01 = scale(fail01, center = T, scale = F),
           fail02 = scale(fail02, center = T, scale = F),
           fail03 = scale(fail03, center = T, scale = F),
           happy = scale(happy, center = T, scale = F),
           lifeSat = scale(lifeSat, center = T, scale = F),
           MLQ = scale(MLQ, center = T, scale = F),
           c19ProSo01 = scale(c19ProSo01, center = T, scale = F),
           c19ProSo02 = scale(c19ProSo02, center = T, scale = F),
           c19ProSo03 = scale(c19ProSo03, center = T, scale = F),
           c19ProSo04 = scale(c19ProSo04, center = T, scale = F),
           c19perBeh01 = scale(c19perBeh01, center = T, scale = F),
           c19perBeh02 = scale(c19perBeh02, center = T, scale = F),
           c19perBeh03 = scale(c19perBeh03, center = T, scale = F),
           c19RCA01 = scale(c19RCA01, center = T, scale = F),
           c19RCA02 = scale(c19RCA02, center = T, scale = F),
           c19RCA03 = scale(c19RCA03, center = T, scale = F)
           )
```

# Analysis
## Confirmatory Factor Analysis
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            para =~ para01 + para02 + para03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            level:2
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            para =~ para01 + para02 + para03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03'
fit <- cfa(model, data = dtCtry, cluster = "coded_country")
# fit <- cfa(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
#            em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)

```

## Multilevel SEM
### Mean Center all relevant vars
```{r}
# mean center the individual scales (this works but want to be sure)
  # dtCtry <- dtCtry %>%
  #   dplyr::mutate_at(vars(matches(
  #     paste(c("aff", "PFS", "fail", "happy", "lifeSat", "MLQ", "c19ProSo"), collapse = "|"), -contains("DO"))), #vars changed
  #     scale, center = T, scale = F) #function for change


# mean center "save" way
dtCtry <- dtCtry %>%
    mutate(affCalm = scale(affCalm, center = T, scale = F),
           affContent = scale(affContent, center = T, scale = F),
           affEnerg = scale(affEnerg, center = T, scale = F),
           affInsp = scale(affInsp, center = T, scale = F),
           affRel = scale(affRel, center = T, scale = F),
           affAnx = scale(affAnx, center = T, scale = F),
           affDepr = scale(affDepr, center = T, scale = F),
           affNerv = scale(affNerv, center = T, scale = F),
           affExh = scale(affExh, center = T, scale = F),
           PFS01 = scale(PFS01, center = T, scale = F),
           PFS02 = scale(PFS02, center = T, scale = F),
           PFS03 = scale(PFS03, center = T, scale = F),
           fail01 = scale(fail01, center = T, scale = F),
           fail02 = scale(fail02, center = T, scale = F),
           fail03 = scale(fail03, center = T, scale = F),
           happy = scale(happy, center = T, scale = F),
           lifeSat = scale(lifeSat, center = T, scale = F),
           MLQ = scale(MLQ, center = T, scale = F),
           c19ProSo01 = scale(c19ProSo01, center = T, scale = F),
           c19ProSo02 = scale(c19ProSo02, center = T, scale = F),
           c19ProSo03 = scale(c19ProSo03, center = T, scale = F),
           c19ProSo04 = scale(c19ProSo04, center = T, scale = F),
           c19perBeh01 = scale(c19perBeh01, center = T, scale = F),
           c19perBeh02 = scale(c19perBeh02, center = T, scale = F),
           c19perBeh03 = scale(c19perBeh03, center = T, scale = F),
           c19RCA01 = scale(c19RCA01, center = T, scale = F),
           c19RCA02 = scale(c19RCA02, center = T, scale = F),
           c19RCA03 = scale(c19RCA03, center = T, scale = F)
           )
```

### Disemp - Consp - Pro-Sociality
#### Stamdard Model
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            # Regression
            consp ~ a1*disemp
            proSo ~ b1*consp + c1*disemp
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            # Regression
            consp ~ d1*disemp
            proSo ~ e1*consp + f1*disemp
            # Indirect and total effects within
            ab:=a1*b1
            totalwith:=ab+c1
            # Indirect and total effects between
            de:=d1*e1
            totalbw:=de+f1'

#fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE, standardized = T)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

#### Control Model
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ a1*disemp + ctrl1*perBeh + ctrl2*RCA
            proSo ~ b1*consp + c1*disemp + ctrl3*perBeh + ctrl4*RCA
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ d1*disemp + ctrl5*perBeh + ctrl6*RCA
            proSo ~ e1*consp + f1*disemp + ctrl7*perBeh + ctrl8*RCA
            # Indirect and total effects within
            ab:=a1*b1
            totalwith:=ab+c1
            # Indirect and total effects between
            de:=d1*e1
            totalbw:=de+f1'

#fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### Disemp - Consp - Individual behavior
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            # Regression
            consp ~ a1*disemp
            perBeh ~ b1*consp + c1*disemp
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
            # Regression
            consp ~ d1*disemp
            perBeh ~ e1*consp + f1*disemp
            # Indirect and total effects within
            ab:=a1*b1
            totalwith:=ab+c1
            # Indirect and total effects between
            de:=d1*e1
            totalbw:=de+f1'

fit <- sem(model, data = dtCtry, cluster = "coded_country")
# fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
#            em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### Disemp - Consp - radical behavior
```{r}
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ a1*disemp
            RCA ~ b1*consp + c1*disemp
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ d1*disemp
            RCA ~ e1*consp + f1*disemp
            # Indirect and total effects within
            ab:=a1*b1
            totalwith:=ab+c1
            # Indirect and total effects between
            de:=d1*e1
            totalbw:=de+f1'

#fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
           em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### Disemp - Consp - multiple DVs
```{r}
# pro-Sociality and RCA (does work)
  model <- 'level:1
            # Latent
            disemp =~ fail01 + fail02 + fail03 
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ a1*disemp
            proSo ~ b1*consp + c1*disemp
            RCA ~ b2*consp + c2*disemp
            level:2
            # Latent
            disemp =~ fail01 + fail02 + fail03
            consp =~ consp01 + consp02 + consp03
            proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
            RCA =~ c19RCA01 + c19RCA02 + c19RCA03
            # Regression
            consp ~ d1*disemp
            proSo ~ e1*consp + f1*disemp
            RCA ~ e2*consp + f2*disemp
            # Indirect and total effects within
            abProSo:=a1*b1
            abRCA:=a1*b2
            totalwithProSo:=abProSo+c1
            totalwithRCA:=abRCA+c2
            # Indirect and total effects between
            deProSo:=d1*e1
            deRCA:=d1*e2
            totalbwProSo:=deProSo+f1
            totalbwRCA:=deRCA+f2'

# all DVs are predicted (does not work)
model <- 'level:1
          # Latent
          disemp =~ fail01 + fail02 + fail03
          consp =~ consp01 + consp02 + consp03
          proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
          RCA =~ c19RCA01 + c19RCA02 + c19RCA03
          # Regression
          consp ~ a1*disemp
          proSo ~ b1*consp + c1*disemp
          perBeh ~ b2*consp + c2*disemp
          RCA ~ b3*consp + c3*disemp
          level:2
          # Latent
          disemp =~ fail01 + fail02 + fail03
          consp =~ consp01 + consp02 + consp03
          proSo =~ c19ProSo01 + c19ProSo02 + c19ProSo03
          perBeh =~ c19perBeh01 + c19perBeh02 + c19perBeh03
          RCA =~ c19RCA01 + c19RCA02 + c19RCA03
          # Regression
          consp ~ d1*disemp
          proSo ~ e1*consp + f1*disemp
          perBeh ~ e2*consp + f2*disemp
          RCA ~ e3*consp + f3*disemp
          # Indirect and total effects within
          abProSo:=a1*b1
          abperBeh:=a1*b2
          abRCA:=a1*b3
          totalwithProSo:=abProSo+c1
          totalwithperBeh:=abperBeh+c2
          totalwithRCA:=abRCA+c3
          # Indirect and total effects between
          deProSo:=d1*e1
          deperBeh:=d1*e2
          deRCA:=d1*e3
          totalbwProSo:=deProSo+f1
          totalbwperBeh:=deperBeh+f2
          totalbwRCA:=deRCA+f3'

fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em")
# fit <- sem(model, data = dtCtry, cluster = "coded_country", optim.method = "em", verbose = T, em.iter.max = 20000,
#            em.fx.tol = 1e-08, em.dx.tol = 1e-04)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

# OLD CODE (BUT WILL BE IMPLEMENTED)
## MultiLevel Regressions
### disemp - Conspiracy with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = disemp.m, y = consp.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(
  tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8'
)

# fit model with fixed slope
  mod1Fix <- lme4::lmer(consp.m ~ disemp.c + (1|coded_country), data = dtCtry)
  summary(mod1Fix)
```

### disemp - Conspiracy with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = disemp.m, y = consp.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod1Rand <- lme4::lmer(consp.m ~ disemp.c + (1 + disemp.c|coded_country), data = dtCtry)
  anova(mod1Fix, mod1Rand) # test diff
  summary(mod1Rand)
  lattice::dotplot(ranef(mod1Rand, postVar=TRUE))
```

### Paranoia - Conspiracy with Fixed Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = para.m, y = consp.m)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()

ggExtra::ggMarginal(tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8')

# fit model with fixed slope
  mod2Fix <- lme4::lmer(consp.m ~ para.c + (1|coded_country), data = dtCtry)
  lattice::dotplot(ranef(mod2Fix, postVar=TRUE))
  summary(mod2Fix)
```

### Paranoia - Conspiracy with Random Slope
```{r}
tmp <- ggplot(dtCtry, aes(x = para.m, y = consp.m, color = coded_country)) +
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_minimal()
plotly::ggplotly(tmp)

# fit model with random slope
  mod2Rand <- lme4::lmer(consp.m ~ para.c + (1 + para.c|coded_country), data = dtCtry)
  anova(mod2Fix, mod2Rand) # test diff
  summary(mod2Rand)
  lattice::dotplot(ranef(mod2Rand, postVar=TRUE))
  # sjPlot::plot_model(mod2Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### disemp -Paranoia - Conspiracy with Fixed Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = disemp.m, y = consp.m)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# 
# ggExtra::ggMarginal(tmp, type = 'histogram', margins = 'both', size = 4, col = '#0F0101', fill = '#37AAE8')


# fit model with random slope
  mod3Fix <- lme4::lmer(consp.m ~ para.c + disemp.c + (1|coded_country), data = dtCtry)
  summary(mod3Fix)
  lattice::dotplot(ranef(mod3Fix, postVar=TRUE))
  #sjPlot::plot_model(mod3Fix, type =  c("re"), show.values = T, value.offset = .5)
```

### disemp -Paranoia - Conspiracy with Random Slope
```{r}
# tmp <- ggplot(dtCtry, aes(x = para.m, y = consp.m, color = coded_country)) +
#   geom_point()+
#   geom_smooth(method = 'lm')+
#   theme_minimal()
# plotly::ggplotly(tmp)

# fit model with random slope
  mod3Rand <- lme4::lmer(consp.m ~ para.c + disemp.c + (1+ para.c + disemp.c |coded_country), data = dtCtry, REML = FALSE,  control = lme4::lmerControl(optimizer ="Nelder_Mead"))
  summary(mod3Rand)
  lattice::dotplot(ranef(mod3Rand, postVar=TRUE))
  #sjPlot::plot_model(mod3Rand, type =  c("re"), show.values = T, value.offset = .5)
```

### Table: Multilevel Approach
```{r}
sjPlot::tab_model(mod1Fix, mod1Rand, mod2Fix, mod2Rand, mod3Fix, mod3Rand)
```


## Multilevel Mediation
### Simple SEM Model
```{r}
model <- '# Model 
            disemp  =~ affCalm + affContent + affEnerg + affInsp + affRel 
            consp =~ happy + lifeSat + MLQ
            para =~ para01 + para02 + para03
          # Regression
            para ~ a*disemp
            consp ~ b*para + c*disemp'
fit <- sem(model, data = dtCtry)
summary(fit, fit.measures=TRUE)
lavaanPlot::lavaanPlot(model = fit, coefs = T, covs = T)
```

### Multilevel SEM Model 1-1-1
First we run a model that has no specified level 2 (only covariances)
```{r}
# Explanation for below (from: https://www.youtube.com/watch?v=GZMXEq7GPvY):
# By adding the same model again on level 2, we are estimating the latent means now
# saturated model on level 2
  model <- 'level:1
            para.c ~ a*disemp.c
            consp.m ~ b*para.c + c*disemp.c
            level:2
            para.c ~~ disemp.c
            para.c ~~ consp.m
            consp.m ~~ disemp.c
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Next we run a model that also has no level 2 specified (only intercepts)
```{r}
# level 2 only intercepts
  model <- 'level:1
            para.c ~ a*disemp.c
            consp.m ~ b*para.c + c*disemp.c
            level:2
            para.c ~ 1
            disemp.c ~1
            consp.m ~ 1
            # Indirect effects
            ab:=a*b
            total:=ab+c'
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
```

Finally we run a model in which the level 2 structure mirrors level 1. This means that on level 2 we model the intercepts (means) and one level 1 the values.
```{r}
# specified model
model <- 'level:1
          para.c ~ a*disemp.c
          consp.m ~ b*para.c + c*disemp.c
          level:2
          para.c ~ d*disemp.c
          consp.m ~ e*para.c + f*disemp.c
          # Indirect and total effects within
          ab:=a*b
          totalwith:=ab+c 
          # Indirect and total effects between
          de:=d*e
          totalbw:=de+f' 
fit <- sem(model, data = dtCtry, cluster = "coded_country")
summary(fit, fit.measures=TRUE)
lavInspect(fit, "icc")
```

##Test longitudinal
